---
title: "Tweetable R Markdown"
author: 
  - first_name: "Alison"
    last_name: "Hill"
    url: https://alison.rbind.io
    affiliation: RStudio
    affiliation_url: https://www.rstudio.com
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
repository_url: https://github.com/apreshill/tweetable-rmd
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
```

<script src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
<script src="https://cdn.jsdelivr.net/npm/create-react-class@15.6.3/create-react-class.min.js"></script>

```{css, echo=FALSE}
.the-tweet a {
  border-bottom: 0px;
}
```

```{js}
// Custom React component that loads embedded Tweet HTML
(function () {
  const Tweet = createReactClass({
    componentDidMount: function() {
      twttr.widgets.load(this.el)
    },
    setRef: function(el) {
      this.el = el
    },
    render: function() {
      const html = { __html: this.props.html }
      return React.createElement('div', { ref: this.setRef, dangerouslySetInnerHTML: html })
    }
  })
  
  window.embeddedTweet = function(html) {
    return React.createElement(Tweet, { html: html, key: html })
  }
})()
```

## The challenge 

```{r}
tweetrmd::tweet_embed(tweetrmd::tweet_url("apreshill", "1367240020944441345"))
```

## Packages

```{r echo=TRUE}
library(rtweet)
library(reactable)
library(tidyverse)
library(httr)
library(htmltools)
library(tidytext)
library(gghighlight)
```


```{r results='hide'}
# get all my mentions
my_mentions <- get_mentions(n = 200)

# here are all rmd tweets
rmd_tweets <- search_tweets("rmarkdown") %>% 
  bind_rows(search_tweets("r markdown"))

rmd_tweets %>% 
  # confirm status id, this is the one!
  filter(status_id == "1367240020944441345") 
```

```{r}
# save number of max buckets for fave counts
max_buckets <- 5
# find all my mentions replying to my original tweet
all_replies <- my_mentions %>% 
  select(status_id, status_in_reply_to_status_id) %>% 
  filter(status_in_reply_to_status_id == "1367240020944441345") %>% 
  pull(status_id) %>% 
  rtweet::lookup_statuses() %>% 
  # rank them
  mutate(favorite_rank = ntile(favorite_count, n = max_buckets))

write_rds(all_replies, "data/all_replies.rds")
```

## Begin the replies!


```{r layout="l-body-outset"}
ggplot(all_replies, aes(created_at)) +
  geom_histogram(fill = "#79BEEE", alpha = .5) +
  theme_minimal() +
  scale_y_continuous(labels = scales::label_number(accuracy = 1))
```

## All replies


```{r}
# make hearts
fave_hearts <- function(favorite_rank, max_buckets = 5) {
  heart_icon <- function(empty = FALSE) {
    tagAppendAttributes(shiny::icon("heart"),
      style = paste("color:", if (empty) "#edf0f2" else "#096B72"),
      "aria-hidden" = "true"
    )
  }
  hearts <- lapply(seq_len(max_buckets), function(i) {
    if (i <= favorite_rank) heart_icon() else heart_icon(empty = TRUE)
  })
  label <- sprintf("%s out of %s", favorite_rank, max_buckets)
  div(title = label, "aria-label" = label, role = "img", hearts)
}
```

```{r include=FALSE}
# troubleshooting hearts
fake_tweets <- tibble(
  state.name[1:5],
  fave_count = sample(1:50, size = 5),
  favorite_rank = ntile(fave_count, n = 5)
)
fake_tweets %>% 
  #mutate(hearts = map(fave_count, fave_hearts)) 
  reactable(
    columns = list(
    favorite_rank = colDef(cell = function(value) fave_hearts(value))
  ))
```



```{r layout="l-body-outset"}
my_pal <- function(x) rgb(colorRamp(c("#E6F3FC", "#79BEEE"))(x), maxColorValue = 255)

all_replies %>% 
  select(
    screen_name, 
    text,
    fave_count = favorite_count,
    favorite_rank
    ) %>%
  reactable(
    
    # global reactable options
    defaultSorted = "fave_count",
    defaultSortOrder = "desc",
    searchable = TRUE,
    highlight = TRUE,
    rowStyle = list(cursor = "pointer"),
    theme = reactableTheme(
      highlightColor = "#FEDB00"),
    
    # formatting individual columns
    columns = 
      list(
        favorite_rank = colDef(
          name = "Favorite Rank", 
          cell = function(value) fave_hearts(value, 
                                             max_buckets = max_buckets),
          minWidth = 150
          ),
        text = colDef(name = "Tweet", 
                      minWidth = 300, 
                      html = TRUE, 
                      class = "the-tweet",
          cell = function(value, index) {
            sprintf('<a href="%s" target="_blank">%s</a>', all_replies$status_url[index], value)
          }),
        fave_count = colDef(name = "Favorites", style = function(value) {
          normalized <- (value - min(all_replies$favorite_count)) / (max(all_replies$favorite_count) - min(all_replies$favorite_count))
          color <- my_pal(normalized)
          list(background = color)
          }),
        # Or using raw HTML
        screen_name = colDef(html = TRUE, cell = function(value, index) {
          sprintf('<a href="%s" target="_blank">%s</a>', all_replies$profile_url[index], value)
          })
      )
  ) 
```



## Top 5 replies

```{r top-replies, layout="l-body-outset"}
top_replies <- all_replies %>% 
  slice_max(favorite_count, n = 5) 

top_replies %>% 
  select(
    screen_name, 
    Favorites = favorite_count,
    status_id
    ) %>%
  mutate(
    embed_url = paste0(
      "https://publish.twitter.com/oembed?url=https://twitter.com/",
      tolower(screen_name),
      "/status/",
      status_id
    ),
    embed_html = map(embed_url, ~ httr::content(httr::GET(.x))$html)
  ) %>%
  select(-status_id, -embed_url) %>% 
  reactable(
    
    # global reactable options
    defaultSorted = "Favorites",
    defaultSortOrder = "desc",
    highlight = TRUE,
    rowStyle = list(cursor = "pointer"),
    theme = reactableTheme(
      highlightColor = "#FEDB00"),
    
    columns = 
      list(
        embed_html = colDef(
          name = "Tweet",
          cell = JS("function(cellInfo) {
            return embeddedTweet(cellInfo.value)
            }"),
          minWidth = 350
          )
        )
      )
```

## Frequently used words

```{r}
remove_reg <- "&amp;|&lt;|&gt;"
rmd_words <- 
  all_replies %>% 
  select(text, favorite_count, retweet_count) %>% 
  filter(!str_detect(text, "^(RT)")) %>%
  mutate(text = str_remove_all(text, remove_reg)) %>%  
  mutate(text = str_remove_all(text, "@(\\w){1,15}")) %>% 
  unnest_tokens(word, text, token = "tweets", strip_url = TRUE) %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         # remove package name
         !(word %in% c("markdown", "r", "rmarkdown")),
         !str_detect(word, "^@"),
         !str_detect(word, "^#"))
```

```{r}
top_words <- rmd_words %>% 
  group_by(word) %>% 
  summarize(uses = n(),
            favorites = median(favorite_count),
            retweets = median(retweet_count)) %>% 
  ungroup() 
  
top_words %>% 
  arrange(uses) %>% 
  slice_max(uses, n = 20) %>%
  mutate(word = factor(word, unique(word))) %>% 
  ggplot(aes(fct_reorder(word, uses), uses)) +
  geom_col(fill = "#096B72", show.legend = FALSE) +
  coord_flip() +
  labs(x = NULL, 
       y = "Number of reply tweets containing each word") +
  theme_minimal() 
```

```{r}
top_words %>% 
  mutate(topuse = ntile(uses, n = 50)) %>% 
  ggplot(aes(x = uses, y = favorites)) +
  geom_point(alpha = .8, color = "#096B72") +
  theme_minimal() +
  gghighlight(topuse == 50, label_key = word) 
```


In this table, find all the words used in the replies, how many replies used each word (`uses`), and the median number of times a tweet using that word was favorited and retweeted.

```{r layout="l-body-outset"}
top_words %>% 
  reactable(
    
    # global reactable options
    searchable = TRUE,
    defaultSorted = "uses",
    defaultSortOrder = "desc",
    highlight = TRUE,
    rowStyle = list(cursor = "pointer"),
    theme = reactableTheme(
      highlightColor = "#FEDB00"),
  
    columns = 
      list(
        favorites = colDef(name = "Median Favorites",
        style = function(value) {
          normalized <- (value - min(top_words$favorites)) / (max(top_words$favorites) - min(top_words$favorites))
          color <- my_pal(normalized)
          list(background = color)
          }),
        retweets = colDef(name = "Median Retweets",
         style = function(value) {
          normalized <- (value - min(top_words$retweets)) / (max(top_words$retweets) - min(top_words$retweets))
          color <- my_pal(normalized)
          list(background = color)
          }))
  )

```

## My retweets

```{r layout="l-body-outset"}
my_quote_rts <- get_timeline(user = "apreshill") %>% 
  filter(is_quote == TRUE) %>% 
  filter(str_detect(text, "EtGnZQa4n5")) %>% 
  select(starts_with("quoted")) 

write_csv(my_quote_rts, "data/my_quote_rts.csv")
my_quote_rts %>% 
  select(quoted_screen_name, 
         quoted_text, 
         Favorites = quoted_favorite_count, 
         Retweets = quoted_retweet_count) %>% 
  reactable(
    # global reactable options
    pagination = FALSE,
    defaultSorted = "Favorites",
    defaultSortOrder = "desc",
    highlight = TRUE,
    theme = reactableTheme(highlightColor = "#FEDB00"),
    
    columns = 
      list(
        quoted_text = colDef(name = "Tweet", 
                             minWidth = 300, 
                             html = TRUE,
                             class = "the-tweet",
          cell = function(value, index) {
            sprintf('<a href="%s" target="_blank">%s</a>', all_replies$status_url[index], value)
          }),
        # Or using raw HTML
        quoted_screen_name = colDef(html = TRUE, cell = function(value, index) {
          sprintf('<a href="%s" target="_blank">%s</a>', all_replies$profile_url[index], value)
          })
      )
  )
```


## Acknowledgments {.appendix}

`r emo::ji("raised_hands")` Thanks to [Allison Horst](https://twitter.com/allison_horst) for the awesome hedgehog illustrations, [Tom Mock](https://twitter.com/thomas_mock) for the reactable help, [Jesse Mostipak](https://twitter.com/kierisi) for the nudge to tweet this in the first place, and [Kelly O'Briant](https://twitter.com/kellrstats) for arranging the tea session that inspired this `r emo::ji("rabbit")` `r emo::ji("hole")`


```{r}
library(metathis)
meta() %>%
  meta_description(
    "Describe R Markdown in a tweet!"
  ) %>% 
  meta_name("github-repo" = "apreshill/tweetable-rmd") %>% 
  meta_viewport() %>% 
  meta_social(
    title = "Tweetable R Markdown",
    url = "https://apreshill.github.io/tweetable-rmd/",
    image = "https://raw.githubusercontent.com/rstudio-education/teaching-in-production/master/slides/images/rmd_flowchart.png",
    image_alt = "Artwork by Allison Horst",
    og_type = "website",
    og_author = "Alison Hill",
    twitter_card_type = "summary",
    twitter_creator = "@apreshill"
  )
```

